---
output: md_document
---
# Plotting

Finally, we want to plot our data to summarise the model from the previous step. [ggplot2](https://cran.r-project.org/web/packages/ggplot2/ggplot2.pdf) is designed to work with tidy data formats and is based on the idea of the [grammar of graphics](https://ramnathv.github.io/pycon2014-r/visualize/ggplot2.html). This concept makes building up graphs from very simple to complex quite straightforward by adding additional layers. However, ggplot2 does have some less than ideal formatting like a grey gridded background. The [cowplot]() package overrides some of these settings to make publication quality plots. Cowplot also has some nice functionality for arranging plots. The [R graphics cookbook](http://www.cookbook-r.com/Graphs/) provides some helpful tutorials for building up plots using ggplot2. 

The features that I find most useful in ggplot2 are:

- Build up plots layer-by-layer
- Can use `facet_wrap()` and `facet_grid()` to create separate plots by a factor in the dataframe

Lets make a plot of the `mtcars` model from the previous step:

```{r}
data(mtcars)
library(ggplot2)
library(cowplot)

p <- ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_point() + 
  geom_smooth(method = "lm")

p
```

We can then use `facet_wrap()` to get a separate plot for each number of cylinders:

```{r}
p <- p + facet_wrap(~cyl)

p
```

The `aes()` part of the call to `ggplot()` allows us to set the aesthetics of the plot, for example the `colour`, based on variables in the dataframe.

> ### Challenge
>
> In a new code chunk in your R Notebook, use ggplot to make a plot of the linear model created in the previous step. Colour the points by species name. 
>
> **HINT** Loading the cowplot package will change the look of the plots to be more suitable for publication.

**Next:** [Additional resources](./next_steps.md)

