---
output: md_document
---
# Tidying model output

In this section, we will run a basic linear model and programatically tidy the output from the model. 

Again using the `mtcars` data, see an example of the output from a linear model:

```{r}
data(mtcars)
lmfit <- lm(mpg ~ wt, data = mtcars)
summary(lmfit)
```

While this summary is useful for assessing the output of a single model, it can become quite difficult once the number of models starts to increase. This is where the [broom](https://cran.r-project.org/web/packages/broom/vignettes/broom.html) package comes in handy. This package provides functions to convert model coefficient estimates, predicted values and residuals, and summary statistics to data frames.

```{r}
library(broom)
# we can view a table of the coefficient estimates and p values
tidy(lmfit)

# we can view a table of the fit statistics
glance(lmfit)
```

The functions from the broom package work on most classes of model output. 

> ### Challenge
>
> Using the `lm()` and `tidy()` functions, fit a linear model relating petal length to petal width and output the table of coefficients.

**Next:** [Plotting](./plotting.md)